Scoring epidemiological forecasts on transformed scales

### 2023-08-24 final submission after reformatting/final-manuscript.tex
Correct typo in caption for Fig 9, add bib entries manually

\begin{figure}[h!]
    \centering
    \caption{Changes in model ratings as measured by relative skill for two-week-ahead predictions for cases (top row) and deaths (bottom row). A: Relative skill scores for case forecasts from different models submitted to the European COVID-19 Forecast Hub computed on the natural scale. B: Change in rankings as determined by relative skill scores when moving from an evaluation on the natural scale to one on the logarithmic scale. Red arrows indicate that the relative skill score deteriorated when moving from the natural to the log scale, green arrows indicate they improved. C: Relative skill scores based on scores on the log scale. D: Difference in relative skill scores computed on the natural and on the logarithmic scale, ordered as in C. E: Relative contributions of the different WIS components (overprediction, underprediction, and dispersion) to overall model scores on the natural and the logarithmic scale. F, G, H, I, J, K: Analogously for deaths.}
    \label{fig:HUB-rank-order}
\end{figure}

@@

\clearpage
\bibliography{final-manuscript.bib}
\end{document}

>>>>

\begin{figure}[h!]
    \centering
    \caption{Changes in model ratings as measured by relative skill for two-week-ahead predictions for cases (top row) and deaths (bottom row). A: Relative skill scores for case forecasts from different models submitted to the European COVID-19 Forecast Hub computed on the natural scale. B: Change in rankings as determined by relative skill scores when moving from an evaluation on the natural scale to one on the logarithmic scale. Red arrows indicate that the relative skill score deteriorated when moving from the natural to the log scale, green arrows indicate they improved. C: Relative skill scores based on scores on the log scale. D: Difference in relative skill scores computed on the natural and on the logarithmic scale, ordered as in C. E: Relative contributions of the different WIS components (overprediction, underprediction, and dispersion) to overall model scores on the natural and the logarithmic scale. F, G, H, I, J: Analogously for deaths.}
    \label{fig:HUB-rank-order}
\end{figure}

@@

\clearpage

\begin{thebibliography}{10}

\bibitem{heldProbabilisticForecastingInfectious2017}
Held L, Meyer S, Bracher J.
\newblock Probabilistic Forecasting in Infectious Disease Epidemiology: The
  13th {{Armitage}} Lecture.
\newblock Statistics in Medicine. 2017;36(22):3443--3460.
\newblock doi:{10.1002/sim.7363}.

\bibitem{doi:10.2105/AJPH.2022.306831}
Reich NG, Lessler J, Funk S, Viboud C, Vespignani A, Tibshirani RJ, et~al.
\newblock Collaborative Hubs: {{Making}} the Most of Predictive Epidemic
  Modeling.
\newblock American Journal of Public Health. 2022;112(6):839--842.
\newblock doi:{10.2105/AJPH.2022.306831}.

\bibitem{timmermannForecastingMethodsFinance2018}
Timmermann A.
\newblock Forecasting {{Methods}} in {{Finance}}.
\newblock Annual Review of Financial Economics. 2018;10(1):449--479.
\newblock doi:{10.1146/annurev-financial-110217-022713}.

\bibitem{gneitingWeatherForecastingEnsemble2005}
Gneiting T, Raftery AE.
\newblock Weather {{Forecasting}} with {{Ensemble Methods}}.
\newblock Science. 2005;310(5746):248--249.
\newblock doi:{10.1126/science.1115255}.

\bibitem{gneitingStrictlyProperScoring2007}
Gneiting T, Raftery AE.
\newblock Strictly {{Proper Scoring Rules}}, {{Prediction}}, and
  {{Estimation}}.
\newblock Journal of the American Statistical Association.
  2007;102(477):359--378.
\newblock doi:{10.1198/016214506000001437}.

\bibitem{goodRationalDecisions1952}
Good IJ.
\newblock Rational {{Decisions}}.
\newblock Journal of the Royal Statistical Society Series B (Methodological).
  1952;14(1):107--114.

\bibitem{winklerScoringRulesEvaluation1996}
Winkler RL, Mu{\~n}oz J, Cervera JL, Bernardo JM, Blattenberger G, Kadane JB,
  et~al.
\newblock Scoring Rules and the Evaluation of Probabilities.
\newblock Test. 1996;5(1):1--60.
\newblock doi:{10.1007/BF02562681}.

\bibitem{bracherEvaluatingEpidemicForecasts2021}
Bracher J, Ray EL, Gneiting T, Reich NG.
\newblock Evaluating Epidemic Forecasts in an Interval Format.
\newblock PLoS computational biology. 2021;17(2):e1008618.
\newblock doi:{10.1371/journal.pcbi.1008618}.

\bibitem{Johansson2019}
Johansson MA, Apfeldorf KM, Dobson S, Devita J, Buczak AL, Baugher B, et~al.
\newblock An Open Challenge to Advance Probabilistic Forecasting for Dengue
  Epidemics.
\newblock Proceedings of the National Academy of Sciences.
  2019;116(48):24268--24274.
\newblock doi:{10.1073/pnas.1909865116}.

\bibitem{cramerCOVID19ForecastHub2020}
Cramer E, Reich NG, Wang SY, Niemi J, Hannan A, House K, et~al.. {{COVID-19
  Forecast Hub}}: 4 {{December}} 2020 Snapshot; 2020.

\bibitem{cramerEvaluationIndividualEnsemble2021}
Cramer E, Ray EL, Lopez VK, Bracher J, Brennen A, Rivadeneira AJC, et~al.
\newblock Evaluation of Individual and Ensemble Probabilistic Forecasts of
  {{COVID-19}} Mortality in the {{US}}.
\newblock medRxiv. 2021; p. 2021.02.03.21250974.
\newblock doi:{10.1101/2021.02.03.21250974}.

\bibitem{sherrattPredictivePerformanceMultimodel2022}
Sherratt K, Gruson H, Grah R, Johnson H, Niehus R, Prasse B, et~al.
\newblock Predictive Performance of Multi-Model Ensemble Forecasts of
  {{COVID-19}} across {{European}} Nation.
\newblock Europe PMC. 2022;doi:{10.1101/2022.06.16.22276024}.

\bibitem{bracherShorttermForecastingCOVID192021}
Bracher J, Wolffram D, Deuschel J, G{\"o}rgen K, Ketterer JL, Ullrich A, et~al.
\newblock Short-Term Forecasting of {{COVID-19}} in {{Germany}} and {{Poland}}
  during the Second Wave \textendash{} a Preregistered Study.
\newblock medRxiv. 2021; p. 2020.12.24.20248826.
\newblock doi:{10.1101/2020.12.24.20248826}.

\bibitem{bracherNationalSubnationalShortterm2021}
Bracher J, Wolffram D, Deuschel J, Goergen K, Ketterer JL, Ullrich A, et~al.
\newblock National and subnational short-term forecasting of {COVID}-19 in
  {Germany} and {Poland}, early 2021.
\newblock {Communications Medicine}. 2022;doi:{10.1038/s43856-022-00191-8}.

\bibitem{CdcepiFlusightforecastdata2022}
CDC. Cdcepi/{{Flusight-forecast-data}}; 2022.
\newblock CDC Epidemic Prediction Initiative.

\bibitem{gosticPracticalConsiderationsMeasuring2020}
Gostic KM, McGough L, Baskerville E, Abbott S, Joshi K, Tedijanto C, et~al.
\newblock Practical Considerations for Measuring the Effective Reproductive
  Number, {{Rt}}.
\newblock medRxiv. 2020;doi:{10.1101/2020.06.18.20134858}.

\bibitem{dushoffSpeedStrengthEpidemic2021}
Dushoff J, Park SW.
\newblock Speed and Strength of an Epidemic Intervention.
\newblock Proceedings of the Royal Society B: Biological Sciences.
  2021;288(1947):20201556.
\newblock doi:{10.1098/rspb.2020.1556}.

\bibitem{bolinLocalScaleInvariance2021}
Bolin D, Wallin J.
\newblock Local Scale Invariance and Robustness of Proper Scoring Rules.
\newblock Statistical Science. 2023;38(1):140--159.
\newblock doi:{10.1214/22-STS864}.

\bibitem{taylorEvaluatingVolatilityInterval1999}
Taylor JW.
\newblock Evaluating Volatility and Interval Forecasts.
\newblock Journal of Forecasting. 1999;18(2):111--128.
\newblock doi:{10.1002/(SICI)1099-131X(199903)18:2<111::AID-FOR713>3.0.CO;2-C}.

\bibitem{mayrLogLevelVAR2015}
Mayr J, Ulbricht D.
\newblock Log versus Level in {{VAR}} Forecasting: 42 Million Empirical
  Answers\textemdash{{Expect}} the Unexpected.
\newblock Economics Letters. 2015;126:40--42.
\newblock doi:{10.1016/j.econlet.2014.11.008}.

\bibitem{loweStochasticRainfallrunoffForecasting2014}
L{\"o}we R, Mikkelsen PS, Madsen H.
\newblock Stochastic Rainfall-Runoff Forecasting: Parameter Estimation,
  Multi-Step Prediction, and Evaluation of Overflow Risk.
\newblock Stochastic Environmental Research and Risk Assessment.
  2014;28(3):505--516.
\newblock doi:{10.1007/s00477-013-0768-0}.

\bibitem{fuglstadDoesNonstationarySpatial2015}
Fuglstad GA, Simpson D, Lindgren F, Rue H.
\newblock Does Non-Stationary Spatial Data Always Require Non-Stationary Random
  Fields?
\newblock Spatial Statistics. 2015;14:505--531.
\newblock doi:{10.1016/j.spasta.2015.10.001}.

\bibitem{Lehmann1950}
Lehmann EL.
\newblock {Some Principles of the Theory of Testing Hypotheses}.
\newblock The Annals of Mathematical Statistics. 1950;21(1):1 -- 26.
\newblock doi:{10.1214/aoms/1177729884}.

\bibitem{diksLikelihoodbasedScoringRules2011}
Diks C, Panchenko V, {van Dijk} D.
\newblock Likelihood-Based Scoring Rules for Comparing Density Forecasts in
  Tails.
\newblock Journal of Econometrics. 2011;163(2):215--230.
\newblock doi:{10.1016/j.jeconom.2011.04.001}.

\bibitem{europeancovid-19forecasthubEuropeanCovid19Forecast2021}
{European Covid-19 Forecast Hub}. European {{Covid-19 Forecast Hub}}; 2021.
\newblock https://covid19forecasthub.eu/.

\bibitem{gneitingMakingEvaluatingPoint2011a}
Gneiting T.
\newblock Making and {{Evaluating Point Forecasts}}.
\newblock Journal of the American Statistical Association.
  2011;106(494):746--762.
\newblock doi:{10.1198/jasa.2011.r10138}.

\bibitem{Flores1986}
Flores BE.
\newblock A pragmatic view of accuracy measurement in forecasting.
\newblock Omega. 1986;14(2):93--98.
\newblock doi:{https://doi.org/10.1016/0305-0483(86)90013-7}.

\bibitem{wallingaHowGenerationIntervals2007}
Wallinga J, Lipsitch M.
\newblock How Generation Intervals Shape the Relationship between Growth Rates
  and Reproductive Numbers.
\newblock Proceedings of the Royal Society B: Biological Sciences.
  2007;274(1609):599--604.
\newblock doi:{10.1098/rspb.2006.3754}.

\bibitem{bartlettSquareRootTransformation1936}
Bartlett MS.
\newblock The {{Square Root Transformation}} in {{Analysis}} of {{Variance}}.
\newblock Supplement to the Journal of the Royal Statistical Society.
  1936;3(1):68--78.
\newblock doi:{10.2307/2983678}.

\bibitem{dunnGeneralizedLinearModels2018}
Dunn PK, Smyth GK.
\newblock Generalized {{Linear Models With Examples}} in {{R}}.
\newblock {Springer}; 2018.

\bibitem{bellegoDealingLogsZeros2022}
Bell{\'e}go C, Benatia D, Pape L. Dealing with {{Logs}} and {{Zeros}} in
  {{Regression Models}}; 2022.

\bibitem{lerchForecasterDilemmaExtreme2015}
Lerch S, Thorarinsdottir TL, Ravazzolo F, Gneiting T. Forecaster's {{Dilemma}}:
  {{Extreme Events}} and {{Forecast Evaluation}}; 2015.

\bibitem{R}
{R Core Team}. R: A Language and Environment for Statistical Computing; 2022.
\newblock Available from: \url{https://www.R-project.org/}.

\bibitem{bosseEvaluatingForecastsScoringutils2022}
Bosse NI, Gruson H, Cori A, {van Leeuwen} E, Funk S, Abbott S.
\newblock Evaluating {{Forecasts}} with Scoringutils in {{R}}.
\newblock arXiv. 2022;doi:{10.48550/arXiv.2205.07090}.

\bibitem{abbottEvaluatingEpidemiologicallyMotivated2022}
Abbott S, Sherratt K, Bosse N, Gruson H, Bracher J, Funk S. Evaluating an
  Epidemiologically Motivated Surrogate Model of a Multi-Model Ensemble; 2022.

\bibitem{boxAnalysisTransformations1964}
Box GEP, Cox DR.
\newblock An {{Analysis}} of {{Transformations}}.
\newblock Journal of the Royal Statistical Society Series B (Methodological).
  1964;26(2):211--252.

\bibitem{srivastavaShapebasedEvaluationEpidemic2022}
Srivastava A, Singh S, Lee F. Shape-Based {{Evaluation}} of {{Epidemic
  Forecasts}}; 2022.

\bibitem{epinow2}
Abbott S, Hellewell J, Sherratt K, Gostic K, Hickson J, Badr HS, et~al..
  EpiNow2: Estimate Real-Time Case Counts and Time-Varying Epidemiological
  Parameters; 2020.

\end{thebibliography}

\end{document}
